Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-10 paper/abstract.tex

\textbf{Context.}
JavaScript is a popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.}
This paper investigates the use of test transplantation and
differential testing for revealing functional bugs in JavaScript
engines.  The former technique runs the regression test suite of a
given engine on another engine.  The latter technique fuzzes existing
inputs and then compares the output produced by different engines with
a differential oracle.
\textbf{Method.}
We conducted experiments with engines from five major players--Apple,
Google, Microsoft, Facebook, and Mozilla--to assess the effectiveness
of test transplantation and differential testing.
\textbf{Results.}
Our results indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc{} and Microsoft's \chakra{}.
To summarize, our results show that
test transplantation and differential testing
are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.

>>>>

\textbf{Context.}
JavaScript is a popular programming language today with several
implementations competing for market dominance. Although a
specification document and a conformance test suite exist to guide
engine development, bugs occur and have important practical
consequences. Implementing correct
engines is challenging because the spec is intentionally
incomplete and evolves frequently.
\textbf{Objective.}
This paper investigates the use of test transplantation and
differential testing for revealing functional bugs in JavaScript
engines.  The former technique runs the regression test suite of a
given engine on another engine.  The latter technique fuzzes existing
inputs and then compares the output produced by different engines with
a differential oracle.
\textbf{Method.}
We conducted experiments with engines from five major players--Apple,
Facebook, Google, Microsoft, and Mozilla--to assess the effectiveness
of test transplantation and differential testing.
\textbf{Results.}
Our results indicate that both techniques revealed several bugs, many of which
confirmed by developers. We reported \noBugsTransplantation{} bugs
with test transplantation (\noBugsTransplantationConfirmed{} of these bugs
confirmed and \noBugsTransplantationFixed{} fixed) and reported
\noBugsDifferentialTesting{} bugs with differential testing
(\noBugsDifferentialTestingConfirmed{} of these confirmed
and \noBugsDifferentialTestingFixed{} fixed). Results indicate that
most of these bugs affected two engines--Apple's
\jsc and Microsoft's \chakra{} (24 and 26 bugs, respectively).
To summarize, our results show that
test transplantation and differential testing
are easy to apply and very effective in
finding bugs in complex software, such as JavaScript engines.
